Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
meth -adding references

[ placeholder for Kathryn to add some stuff! ]

@@

-   Feature overlap. see [@10.1186/s12864-022-08781-5](#refs) Bedtools for quantitative assessment and IGV for visual assessment are valuable for this.

>>>>

```{r meth-vert, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/vert_methyl_distr.png")
```
[ placeholder for Kathryn to add some stuff! ]

@@

-   Feature overlap. example: [@10.3389/fmars.2020.00225](#refs) Bedtools is excellent for quantitative assessment of feature overlap and IGV is good for visual assessment.
